Correlation of filter methods

### 2019-06-30 analysis/filter-correlation.Rmd
workflowr::wflow_publish("analysis/filter-correlation.Rmd")

source(here::here("code/99-packages.R"))
sourceDirectory("R")

# load drake objects
loadd(
  fv_nri_car, fv_nri_info.gain, fv_nri_gain.ratio,
  fv_nri_symuncert, fv_nri_relief,
  fv_nri_rank, fv_nri_cor,
  fv_nri_mrmr,
  fv_nri_cmim, fv_nri_var,

@@

  fv_nri_info.gain5, fv_nri_info.gain10,
  fv_nri_info.gain15, fv_nri_info.gain20,
  fv_nri_info.gain25, fv_nri_info.gain30
)
library("rgdal")
```

@@

Spearman's rank correlation is used because we compare rankings against each other.

@@

```{r correlation-filter-vi, warning=FALSE, dev = c("png", "pdf")}
# combine filter values

@@

```{r filter-correlation-3, warning=FALSE}
# combine filter values

@@

```{r filter-correlation-5, echo = FALSE}
file_move("docs/figure/filter-correlation.Rmd/correlation-nbins-1.pdf",
          "code/98-paper/journal/")
file_move("docs/figure/filter-correlation.Rmd/correlation-filter-vi-1.pdf",
          "code/98-paper/journal/")
```

>>>>

#source(here::here("code/99-packages.R"))
library("dplyr")
library("tidyr")
library("ggcorrplot")
library("purrr")
library("glue")
library("fs")
R.utils::sourceDirectory("R")

# load drake objects
drake::loadd(
  fv_nri_car, fv_nri_info.gain, fv_nri_gain.ratio,
  fv_nri_symuncert, fv_nri_relief,
  fv_nri_rank, fv_nri_cor,
  fv_nri_mrmr,
  fv_nri_cmim, fv_nri_var,

@@

  fv_nri_info.gain5, fv_nri_info.gain10,
  fv_nri_info.gain15, fv_nri_info.gain20,
  fv_nri_info.gain25, fv_nri_info.gain30
)
```

@@

Spearman's rank correlation is used because rankings are compared.

@@

```{r filter-correlation-1, warning=FALSE}
# combine filter values

@@

```{r filter-correlation-nri, dev = c("png", "pdf"), warning=FALSE}
# combine filter values

@@

```{r filter-correlation-5, echo = FALSE}
# file_move("docs/figure/filter-correlation.Rmd/correlation-nbins-1.pdf",
#           "code/98-paper/journal/")
# file_move("docs/figure/filter-correlation.Rmd/correlation-filter-nri-1.pdf",
#           "code/98-paper/journal/")
```
